

\documentclass[a4paper,11pt]{article}
\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}
\usepackage{CJK}

\usepackage{hyperref} % Use the Charter font for the document text
%\usepackage[UTF8]{ctex}
\usepackage{fullpage}

\usepackage{graphicx}


\begin{document}\thispagestyle{empty}
\begin{CJK}{UTF8}{gbsn}

\centerline{\Large \bf Syllabus}

\begin{description}
\item{\bf Course name:} Quantum Field Theory II (PHYS130106.01)
\item{\bf Instructor:} Satoshi Nawata, Physics S422, Jiangwan \href{mailto:snawata@fudan.edu.cn}{snawata@fudan.edu.cn}
\item{\bf Teaching Assistant:} Hao Wang, \href{mailto:19110190011@fudan.edu.cn}{19110190011@fudan.edu.cn}
\item{\bf Hours:}  Monday 13:30 -- 16:10
\item{\bf Place:}  \href{https://live.bilibili.com/21873644}{Bilibili}
\item{\bf Office hour:} Whenever, but email me.
\item{\bf Prerequisites:} Quantum Fied Theory I, Quantum mechanics, Electrodynamics, Classical Mechanics
\item{\bf About the course:}

Based on what we have learned in QFTI in Fall 2019, we will continue to learn new concepts and techniques of quantum field theory. We will study renormalization group flow, beta-functions, and Wilsonian effective action. In addition, we introduce to quantization of non-Abelian gauge theories and spontaneously symmetry breaking.
 With these preparations, we will understand how QFT can describe the Higgs mechanism and the Standard Model of particle physics. If time permits, we will learn anomaly and some aspects of QCD.

 We will start from chapter 9 of Peskin and Schroeder, and will cover selected (not all) chapters.

Due to the outbreak, we will do live streaming at \href{https://live.bilibili.com/21873644}{https://live.bilibili.com/21873644} during 13:30 -- 16:10, Monday. All the recorded videos will be uploaded to the \href{https://space.bilibili.com/1628225/}{account} of the TA, Wang Hao.

\item{\bf Main content:}
\begin{itemize}
\item Path integral formulation
\item General aspects of renormalization
\item Wilsonian renormalization group flow
\item Quantization of Yang-Mill theory
\item Spontaneously symmetry breaking
\item Higgs mechanism and the Standard Model of particle physics
\item Some other advanced topics
\end{itemize}

\item{\bf Main textbook:}

An Introduction to Quantum Field Theory. Michael E. Peskin, Daniel V. Schroeder

\item{\bf Supplementary textbooks:}

Quantum Field Theory, Mark Srednicki

Quantum field theory and the standard model, Matthew Dean Schwartz.

The Quantum Theory of Field, Steven Weinberg

\item{\bf Grade evaluation:} Grade will be determined based on homework sets (60\%) given every other week and the final test (40\%).


\end{description}


\end{CJK}


\end{document}
